---
title: "summary_analysis"
format: html
editor: visual
---

# Summary Analysis

## Plotting Results

```{r}
library(ggplot2) 
jan_plot <- ggplot(jan_data, aes(x=year, y=temp_C, color=site_no))+ 
  geom_point(alpha = 0.3, size =1)+ 
  geom_smooth(method="glm", se=TRUE)+ 
  labs(title= "January Temperature Trends Over Time by Site", 
       x="Year", y="Temperature (ºC)", color = "Site")+ 
  theme_minimal()
```

```{r}
library(ggplot2) 
jul_plot <- ggplot(july_data, aes(x=year, y=temp_C, color=site_no))+ 
  geom_point(alpha = 0.3, size =1)+ geom_smooth(method="glm", se=TRUE)+ 
  labs(title= "July Temperature Trends Over Time by Site", 
       x="Year", y="Temperature (ºC)", color = "Site")+ 
  theme_minimal()
```

```{r}
jan_plot + jul_plot
```

## Analysis of findings

We compared the rate annual water temperature increase across the three sites in January and July. Fitting a Generalized Linear model to the data, we were able to compare whether warming trends were significantly different compared to site 14166000 (baseline).

In January, though the baseline site was initially the warmest, both of the other sites exhibited a rate of warming significantly faster than than the baseline. By 2018, site 14211720 surpassed the baseline site as the warmest.

In July, the baseline site was initially the coolest and remained so for the duration of the study period. Though site 1411720 had a warmer temperature than the baseline, the rate of warming was not significantly different. On the other hand, site 14211010 was initially exhibited similar temperature to the baseline site, but exhibited a rate of warming significantly faster than the baseline, causing the temperatures to diverge over the course of the study period.

In summary, all sites exhibited warming trends. In January, sites 14211720 & 14211010 exhibit warming trends faster than the baseline. In July, site 14211720 is warming at a similar rate to the baseline, whereas site 14211010 is warming faster.
